Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-13 chapters/paper2.tex
Changes 1. Added paper attribution as footnotes 2. Fixed some language in lit review

\section{Introduction}

Sections of this chapter appear in a manuscript submitted to Springerlink as part of the International Conference on Computational 
Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
% [author and/or editor(s) of contribution], [volume and/or contribution title], [year of publication], [publisher (as it appears on our copyright page)] \
reproduced with permission of Palgrave Springer Nature.

@@

\section{Results}\label{sec:results_p2}
\subsection{Kinetic arrest}
\label{section:hysteresis_curve}

@@

The domain sizes characterized in Figure~\ref{fig:hysteresis_curve} demonstrates that as the field is increased, domain size increases, indicating coarsening 
of the fluid domains in the bijel. Chapter 4 showed that application of magnetic fields cause reordering of particles at interfaces towards the
direction of the applied field, making the particle monolayer have nematic ordering. In the case of already formed bijels,
this reorientation reduces the interface area stabilized, facilitating local unjamming and domain growth. In contrast, when the field strength is reduced, 
the domain size does not revert to its original value, suggesting that the microstructure remains kinetically arrested in the coarsened configuration.

@@

\subsection{Switching a field onto a bijel with disordered particles}
\subsubsection{Field strength dependence on domain size}
\label{section:field-strength-dependence-on-domain-size}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_on.png} 
    \caption{Plots of the time evolution of the normalized domain size \(L/R\) (markers) and nematic order parameter 
             \(S\) (lines) for bijels stabilized by oblate (left, \(\alpha = 0.5\)) and prolate (right, \(\alpha = 2.0\)) ellipsoidal particles under varying 
             magnetic field strengths. Here, \(R = 7.9\) is the volume-equivalent sphere radius.} 
    \label{fig:domain_size-field_on} 
\end{figure}

The results show that applying a magnetic field to bijels 
initially formed without one induces domain coarsening, with the final domain size increasing by up to 5.2\% for oblate and 2.5\% for 
prolate particle-stabilized systems.
In both oblate and prolate systems, domain coarsening follows a characteristic three-stage evolution: an initial slow growth phase, a period of rapid 
coarsening, and eventual plateauing as the structure reaches a new jammed configuration. Even in the absence of a magnetic field (\(\bar{B}_z = 0\)), 
domain growth is observed driven by steric rearrangement of interfacial particles, consistent 
with findings by Günther et al.~\cite{gunther_timescales_2014}. Notably, the initiation of domain coarsening under applied magnetic fields is more rapid 
for bijels stabilized by oblate particles compared to prolate systems. However, the rejamming process takes longer.

In the absence of magnetic fields, a slight increase in $S(t)$ is observed, consistent with the sterically driven reorientation of particles at the interface.
\cite{gunther_timescales_2014} Upon application of a magnetic field, the curves for \(S(t)\) increase before plateauing, indicating the parameter has reached
its saturation value. Notably at stronger field strengths, $S(t)$ precedes the increase in domain size for both particle shapes analyzed. Overall, these results 
confirm that domain coarsening in magnetically responsive bijels occurs as a result of applied magnetic fields, with the degree of change observed dependent 
on the strength of the applied field.

@@

Figure~\ref{fig:domain_size_aniso-field_on} shows that the application of a magnetic field induces clear domain size anisotropy in bijels stabilized by both oblate 
and prolate particles. Even at zero field, a small degree of anisotropy is observed, which increases substantially with rising field strength. For oblate particles, 
the domain sizes perpendicular (\(L_\perp\)) and parallel (\(L_\parallel\)) to the applied field increase by approximately 73\% and 7\%, respectively. In contrast, 
for prolate particles, \(L_\perp\) increases by 10\%, while \(L_\parallel\) increases by 44\%. These results indicate that the dominant direction of coarsening 
depends on particle morphology: oblate particles promote greater coarsening perpendicular to the field, while prolate particles favor coarsening parallel to the 
field. This trend reflects how particles reorient in response to the applied magnetic field. As particles unjam and rejam 
at the interface, they adopt morphology- and field-dependent orientations that result in directionally biased surface coverage, manifesting as anisotropic domain 
growth.

@@

From Figure \ref{fig:nematic-field_on}, as field strength increases, particles exhibit earlier and more pronounced alignment, with \( S \) approaching unity 
for \( \bar{B} = 1.0 \), indicating strong global nematic order. In contrast, systems with no applied field (\( \bar{B} = 0 \)) remain disordered throughout, 
with low \( S \) values. The time-dependent development of nematic ordering reflects the interplay between magnetic torque and interfacial mechanics. 
The increase in \( S \) suggests a process of unjamming and re-jamming at the fluid-fluid interface caused by the magnetic field inducing rotational 
motion of the dipolar particles, overcoming initial interfacial jamming and allowing particles to realign to the field. As alignment 
progresses, the particles re-jam. In Chapters 4 and 5, the application of the magnetic field modified the angle of the particle to the interface and the
local packing of the particles. This was caused by orientational of the particles to the magnetic field causing direction dependent cessation of coarsening.
To understand how the rotation of particles affects the particle monolayer, the interfacial angle $\langle \psi \rangle$ is analyzed to understand
how the nematic transition takes place at the interface. $\langle \psi \rangle$ is calculated in the same method as that used to generate Figure \ref{fig:psi_time} 
in Chapter 4, with the results presented in Figure \ref{fig:interface_angle-field_on}.

@@

\subsection{Decreasing the applied field}
\label{decreasing-the-applied-field}

@@

Gunther et al. also showed that bijels stabilized by ellipsoidal particles exhibited timescales 
of response distinct from bijels stabilized by spherical particle due to steric effects between ellipsoidal particles.
Therefore, this section will seek to understand to what extent the initial particle order affects the 
bijel's capacity to relax or restructure upon removal of the field. To explore this, 
we now examine the post-stimulus structural response of bijels formed under different field conditions 
\(\bar{B}_{\text{template}} = 0.0, 0.2, 0.5, 1.0\). After allowing each structure to fully stabilize under a 
constant magnetic field, we switch off the field and observe the subsequent time evolution of both the 
microstructure and interfacial particle behavior over a duration of \(t = 10^5 \Delta t\). This analysis aims to 
clarify the mechanisms that underpin the apparent irreversibility captured in the hysteresis response and further 
assess the role of processing history in bijel stability.

@@

Figure \ref{fig:microstructure_viz-field_down} shows that in 
both cases, the bulk microstructure remains effectively unchanged over the course of the simulation, highlighting the 
kinetic stability and arrested nature of the bijel.
However, closer inspection of the interfacial particle arrangement reveals that in the
\(\bar{B}: 0.2 \rightarrow 0.0\) case, the particles retain a degree of orientational order, although slight deviations 
from the field-aligned configuration begin to emerge. In contrast, for \(\bar{B}: 1.0 \rightarrow 0.0\), where the 
initial nematic order was stronger, the system exhibits more apparent disorganization by the final time step. This 
suggests that while the jammed interface resists large-scale rearrangement, there is a gradual relaxation of particle 
orientations in the absence of the aligning field. The extent of this relaxation correlates with the initial field strength when 
the field is removed. We probe the effect of these reorientations by calculating the time evolution of the domain size
in Figure \ref{fig:domain_size-field_down}

@@

\section{Conclusions}

@@

When investigating the effect of the application of magnetic fields, our results revealed that applying magnetic fields post-formation induces domain coarsening up to 5\%, with 
field-induced anisotropy dependent on particle shape. Oblate particles exhibited growth primarily in the perpendicular direction by up to 60\%, while prolate particles showed 
coarsening along the field direction up to 40\%, both accompanied by a decrease in tortuosity. These changes arise from particle reorientation to the field, followed by 
local unjamming and interfacial rearrangement before re-jamming occurs, as characterized using the average interface angle of the particles and the 
Steinhardt bond orientational order parameter. In contrast, removing the magnetic field had little effect 
on bijel structure. Domain size and anisotropy remained largely unchanged, regardless of initial particle order. While minor relaxation in particle alignment was observed, 
capillary forces alone were insufficient to drive significant structural reorganization.

These results show that rapid reorientation of the particle stabilizers is necessary to induce structural response in bijels. This is illustrated through structural response
of bijels occurring upon application of the field, causing rapid realignment of particles to the applied field direction while slow realignment of particles away from
the field when switching the field off generated no meaningful changes in the microstructure.

While our simulations offer valuable insights into the tunability of bijels, they were limited to a single set of fluid and particle parameters. Future work could explore the 
effects of particle size, volume fraction, interparticle forces, and field orientation or gradients, all of which may unlock additional control over bijel structure.
Ultimately, this study establishes a foundation for stimuli-responsive bijels, showing how particle-level interactions and monolayer dynamics translate into controllable, 
application-relevant changes in material microstructure.

>>>>

\section[Introduction]{Introduction\protect\footnote{Sections of this chapter appear in a manuscript submitted to Springerlink as part of the International Conference on Computational 
Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
reproduced with permission of Palgrave Springer Nature.}}

% [author and/or editor(s) of contribution], [volume and/or contribution title], [year of publication], [publisher (as it appears on our copyright page)] \

@@

\section{Results}
% \section[Results]{Introduction\protect\footnote{Sections of this chapter appear in a manuscript submitted to Springerlink as part of the International Conference on Computational 
% Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
% reproduced with permission of Palgrave Springer Nature.}}
% \label{sec:results_p2}

\subsection{Kinetic arrest}
\label{section:hysteresis_curve}

@@

The domain sizes characterized in Figure~\ref{fig:hysteresis_curve} demonstrates that as the field is increased, domain size increases, indicating coarsening 
of the fluid domains in the bijel. Chapter 4 showed that application of magnetic fields cause reordering of particles at interfaces towards the
direction of the applied field, enforcing nematic order in the particle monolayer. In the case of already formed bijels,
this reorientation reduces the interface area stabilized, facilitating local unjamming and domain growth. In contrast, when the field strength is reduced, 
the domain size does not revert to its original value, suggesting that the microstructure remains kinetically arrested in the coarsened configuration.

@@

\subsection{Applying a field onto a bijel with disordered particles}
\subsubsection{Field strength dependence on domain size}
\label{section:field-strength-dependence-on-domain-size}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_on.png} 
    \caption{Plots of the time evolution of the normalized domain size \(L/R\) (markers) for bijels stabilized by oblate (left, \(\alpha = 0.5\)) 
             and prolate (right, \(\alpha = 2.0\)) ellipsoidal particles under varying magnetic field strengths. Here, \(R = 7.9\) is the volume-equivalent sphere radius.} 
    \label{fig:domain_size-field_on} 
\end{figure}

The results show that applying a magnetic field to bijels 
initially formed without one induces domain coarsening, with the final domain size increasing by up to 5.2\% for oblate and 2.5\% for 
prolate particle-stabilized systems.
In both oblate and prolate systems, domain coarsening follows a characteristic three-stage evolution: an initial slow growth phase, a period of rapid 
coarsening, and eventual plateauing as the structure reaches a new jammed configuration. Even in the absence of a magnetic field (\(\bar{B}_z = 0\)), 
domain growth is observed driven by steric rearrangement of interfacial particles, consistent 
with findings by Günther et al.~\cite{gunther_timescales_2014}.

@@

Figure~\ref{fig:domain_size_aniso-field_on} shows that the application of a magnetic field induces domain size anisotropy in bijels stabilized by both oblate 
and prolate particles. Even at zero field, a small degree of anisotropy is observed, which increases substantially with rising field strength. For oblate particles, 
the domain sizes perpendicular (\(L_\perp\)) and parallel (\(L_\parallel\)) to the applied field increase by approximately 73\% and 7\%, respectively. In contrast, 
for prolate particles, \(L_\perp\) increases by 10\%, while \(L_\parallel\) increases by 44\%. These results indicate that the dominant direction of coarsening 
depends on particle morphology: oblate particles promote greater coarsening perpendicular to the field, while prolate particles favor coarsening parallel to the 
field. This trend reflects how particles reorient in response to the applied magnetic field. As particles unjam and rejam 
at the interface, they adopt morphology- and field-dependent orientations that result in directionally biased surface coverage, manifesting as anisotropic domain 
growth.

@@

From Figure \ref{fig:nematic-field_on}, as field strength increases, particles exhibit earlier and more pronounced alignment, with \( S \) approaching unity 
for \( \bar{B} = 1.0 \), indicating strong global nematic order. In contrast, systems with no applied field (\( \bar{B} = 0 \)) remain disordered throughout, 
with low \( S \) values. The time-dependent development of nematic ordering reflects the interplay between magnetic torque and interfacial mechanics. 
The increase in \( S \) demonstrates the application of a constant magnetic field causes particle to rotate at the interface to align with the magnetic field.
Linking the alignment of the particles to the domain size change showed in Figure \ref{fig:domain_size-field_on}, the rotation of particles to the magnetic field 
overcomes the initial interfacial jamming. allowing particles to realign to the field. As alignment 
progresses, the particles re-jam. In Chapters 4 and 5, the application of the magnetic field modified the angle of the particle to the interface and the
local packing of the particles. This was caused by orientational of the particles to the magnetic field causing direction dependent cessation of coarsening.
To understand how the rotation of particles affects the particle monolayer, the interfacial angle $\langle \psi \rangle$ is analyzed to understand
how the nematic transition takes place at the interface. $\langle \psi \rangle$ is calculated in the same method as that used to generate Figure \ref{fig:psi_time} 
in Chapter 4, with the results presented in Figure \ref{fig:interface_angle-field_on}.

@@

\subsection{Switching off an applied field}
\label{decreasing-the-applied-field}

@@

Gunther et al. also showed that bijels stabilized by ellipsoidal particles exhibited timescales 
of response distinct from bijels stabilized by spherical particle due to steric effects between ellipsoidal particles.
Therefore, this section will seek to understand to what extent the initial particle order affects the 
bijel's capacity to relax or restructure upon removal of the field. To explore this, 
we now examine the post-stimulus structural response of bijels formed under different field conditions 
\(\bar{B}_{\text{template}} = 0.0, 0.2, 0.5, 1.0\). After allowing each structure to fully stabilize under a 
constant magnetic field, we switch off the field and observe the subsequent time evolution of both the 
microstructure and interfacial particle behavior over a duration of \(t = 10^5 \Delta t\). This analysis aims to 
clarify the mechanisms that underpin the apparent irreversibility captured in the hysteresis response and further 
assess the role of the particles in bijel stability.

@@

Figure \ref{fig:microstructure_viz-field_down} shows that in 
both cases, the bulk microstructure remains effectively unchanged over the course of the simulation, highlighting the 
kinetic stability and arrested nature of the bijel.
However, closer inspection of the interfacial particle arrangement reveals that in the
\(\bar{B}: 0.2 \rightarrow 0.0\) case, the particles retain a degree of orientational order, although slight deviations 
from the field-aligned configuration begin to emerge. In contrast, for \(\bar{B}: 1.0 \rightarrow 0.0\), where the 
initial nematic order was stronger, the particles exhibits more apparent disorganization by the final time step. This 
suggests that while the jammed interface resists large-scale rearrangement, there is a gradual relaxation of particle 
orientations in the absence of the aligning field. The extent of this relaxation correlates with the initial field strength when 
the field is removed. We probe the effect of these reorientations by calculating the time evolution of the domain size
in Figure \ref{fig:domain_size-field_down}

@@

\section{Conclusion}
% \section[Conclusion]{Conclusion\protect\footnote{Sections of this chapter appear in a manuscript submitted to Springerlink as part of the International Conference on Computational 
% Science (ICCS) 2025 in the Computing and Data Science for Materials Discovery and Design track, submission number 259 and is
% reproduced with permission of Palgrave Springer Nature.}}

@@

When investigating the effect of the application of magnetic fields, our results revealed that applying magnetic fields post-formation induces domain coarsening up to 5\%, with 
field-induced anisotropy dependent on particle shape. These changes arise from particle reorientation to the field, followed by 
local unjamming and interfacial rearrangement before re-jamming occurs, as characterized using the average interface angle of the particles and the 
Steinhardt bond orientational order parameter. In contrast, removing the magnetic field had little effect 
on bijel structure. Domain size and anisotropy remained largely unchanged, regardless of initial particle order. While minor relaxation in particle alignment was observed, 
capillary forces alone were insufficient to drive significant structural reorganization.

These results show that rapid coordinated reorientation of the particle stabilizers is necessary to induce structural response in bijels. This is illustrated through structural response
of bijels occurring upon application of the field, causing rapid realignment of particles to the applied field direction while slow realignment of particles away from
the field when switching the field off generated no meaningful changes in the microstructure.

While our simulations offer insights into the tunability of bijels, they were limited to a single set of fluid and particle parameters. Future work could explore the 
effects of particle size, volume fraction, interparticle forces, and field orientation or gradients, all of which may unlock additional control over bijel structure.
Ultimately, this study establishes a foundation for stimuli-responsive bijels, showing how particle-level interactions and monolayer dynamics translate into controllable, 
application-relevant changes in material microstructure.

### 2025-04-13 chapters/paper3.tex
Changes 1. Added paper attribution as footnotes 2. Fixed some language in lit review

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/stress-time_compare.png} 
    \caption{Time evolution of the shear stress of bijels stabilized with ellipsoidal particles as a function of the applied strain rate as
             a function of the initial microstructure and applied magnetic field. The observed stress response is difficult to say when a steady
             state is reached, with pseudo-steady states being obtained from the regions with the circular markers.} 
    \label{fig:stress_time} 
\end{figure}

Figure \ref{fig:stress_time} demonstrates that a definitive steady-state shear stress is not reached within the simulated timeframes across all conditions. 
This absence of steady-state behavior is attributed to the continued coarsening of the bicontinuous domains and the progressive reorientation of interfacial 
particles under shear \cite{tavacoli_novel_2011, macmillan_rheological_2019}. Tavacoli et al.\ showed that mechanical perturbation of bijels, such as the 
insertion of a needle to measure yield stress, resulted in irreversible structural deformation, particularly in ethanediol/nitromethane systems 
\cite{tavacoli_novel_2011}. Similarly, Macmillan et al.\ observed that repeated shearing of bijels synthesized by direct mixing led to degraded mechanical 
performance over time, suggesting a link between structural evolution and rheological response \cite{macmillan_rheological_2019}. To characterize the rheology 
of these evolving systems, we identify pseudo-steady-state regions within the stress-time profiles, defined as intervals where the rate of change of shear 
stress is minimal and persists for the longest continuous duration. Within these regions, the stress response is fitted to the applied shear rate using a 
Herschel-Bulkley model:

\begin{equation}
    \sigma_{xz} = \sigma_{y} + K\dot{\gamma}^{n}    
\end{equation}

In the Herschel-Bulkley model, $\sigma_{xz}$ denotes the computed shear stress, $\sigma_y$ is the yield stress, $K$ represents the flow consistency index, 
and $n$ is the flow index characterizing the degree of shear thinning. In certain cases, simulations conducted at the lowest shear capillary number 
($Ca_s = 10^{-6}$) exhibited insufficient stress resolution or high variability, and were excluded from model fitting where appropriate. For each case, 
$\sigma_{xz}$ is extracted from the pseudo-steady-state region of the stres-time curves, while the corresponding shear rate $\dot{\gamma}$ is derived from 
the imposed capillary number, $Ca_s$. The resulting fits for the various bijel systems are presented in Figure~\ref{fig:stress_strain}.

@@

Figure~\ref{fig:stress_strain} presents the shear stress $\sigma_{xz}$ as a function of shear rate $\dot{\gamma}$ for bijels stabilized by oblate ($\alpha = 0.5$) 
and prolate ($\alpha = 2.0$) ellipsoidal particles, fitted using the Herschel-Bulkley model. In both cases, the curves exhibit nonlinear scaling with $\dot{\gamma}$, 
confirming a non-Newtonian, shear-thinning response. For bijels stabilized by oblate particles, the stress-strain curves are more widely separated, indicating 
greater sensitivity to the initial microstructural configuration induced by magnetic field history. Specifically, increased orientational ordering—achieved through 
magnetic pre-alignment—correlates with a reduced yield stress, as observed by the downward shift of the stress curves. In contrast, bijels stabilized by prolate 
particles exhibit more closely clustered stress responses across different magnetic conditions, suggesting a reduced dependence on field history. Interestingly, 
for the prolate case, the stress response under persistent ordering ($\bar{B}:1 \rightarrow 1$) exceeds that of disordered systems, implying that aligned rod-like 
particles enhance interfacial resistance to shear. These trends highlight the contrasting rheological behaviors imparted by particle shape and the role of 
field-induced anisotropy in modulating mechanical response. Quantitative fit parameters obtained from the Herschel-Bulkley model are provided in 
Table~\ref{table:rheology_fit}.

>>>>

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/stress-time_compare.png} 
    \caption{Time evolution of the shear stress of bijels stabilized with ellipsoidal particles as a function of the applied strain rate as
             a function of the initial microstructure and applied magnetic field. The observed stress response is difficult to say when a steady
             state is reached, with pseudo-steady states being obtained from the regions demarcated with the circular markers.} 
    \label{fig:stress_time} 
\end{figure}

Figure \ref{fig:stress_time} demonstrates that a definitive steady-state shear stress is not reached within the simulated timeframes across all conditions. 
This absence of steady-state behavior is attributed to the continued coarsening of the bicontinuous domains and the progressive reorientation of interfacial 
particles under shear \cite{tavacoli_novel_2011, macmillan_rheological_2019}. Tavacoli et al. showed that mechanical perturbation of bijels, such as the 
insertion of a needle to measure yield stress, resulted in irreversible structural deformation, particularly in ethanediol/nitromethane systems 
\cite{tavacoli_novel_2011}. Similarly, Macmillan et al. observed that repeated shearing of bijels synthesized by direct mixing led to degraded mechanical 
performance over time, suggesting a link between structural evolution and rheological response \cite{macmillan_rheological_2019}. To characterize the rheology 
of these evolving systems, we identify pseudo-steady-state regions within the stress-time profiles, defined as intervals where the rate of change of shear 
stress is minimal and persists for the longest continuous duration. Within these regions, the stress response is fitted to the applied shear rate using a 
Herschel-Bulkley model:

\begin{equation}
    \sigma = \sigma_{y} + K\dot{\gamma}^{n}    
\end{equation}

In the Herschel-Bulkley model, $\sigma$ denotes the computed shear stress, $\sigma_y$ is the yield stress, $K$ represents the flow consistency index, 
and $n$ is the flow index characterizing the degree of shear thinning. In certain cases, simulations conducted at the lowest shear capillary number 
($Ca_s = 10^{-6}$) exhibited insufficient stress resolution or high variability, and were excluded from model fitting where appropriate. For each case, 
$\sigma$ is extracted from the pseudo-steady-state region of the stress-time curves, while the corresponding shear rate $\dot{\gamma}$ is derived from 
the imposed capillary number, $Ca_s$. The resulting fits for the various bijel systems are presented in Figure~\ref{fig:stress_strain}.

@@

Figure~\ref{fig:stress_strain} presents the shear stress $\sigma_{xz}$ as a function of shear rate $\dot{\gamma}$ for bijels stabilized by oblate ($\alpha = 0.5$) 
and prolate ($\alpha = 2.0$) ellipsoidal particles, fitted using the Herschel-Bulkley model. In both cases, the curves exhibit sublinear scaling with $\dot{\gamma}$, 
confirming a non-Newtonian, shear-thinning response. For bijels stabilized by oblate particles, the stress-strain curves are more widely separated, indicating 
greater sensitivity to the initial microstructural configuration induced by magnetic field history. Specifically, increased orientational ordering—achieved through 
magnetic pre-alignment—correlates with a reduced yield stress, as observed by the downward shift of the stress curves. In contrast, bijels stabilized by prolate 
particles exhibit more closely clustered stress responses across different magnetic conditions, suggesting a reduced dependence on field history. Interestingly, 
for the prolate case, the stress response under persistent ordering ($\bar{B}:1 \rightarrow 1$) exceeds that of disordered systems, implying that aligned rod-like 
particles enhance interfacial resistance to shear. These trends highlight the contrasting rheological behaviors imparted by particle shape and the role of 
field-induced anisotropy in modulating mechanical response. Quantitative fit parameters obtained from the Herschel-Bulkley model are provided in 
Table~\ref{table:rheology_fit}.
